---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cosmo
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkg=c("tm")
sapply(pkg, require, character=T)
```


<h1>Text Mining</h1><ol type="I">

<h2><li>Handling and Processing Strings</li></h2><ol type="1">

<h3><li>Reading in Text Data</li></h3>
read text data in table format

read.table(): main function to read file in table format
read.csv(): reads csv files separated by a comma","
read.csv2(): reads csv files separated by a semicolon";"
read.delim(): reads files separated by tabs"\t"
read.delim2(): similar to read.delim()
read.fwf(): read fixed width format files

stringAsFactors=F

Raw text data
readLines()


<h3><li>String Manipulation</li></h3>


grep
gsub
gregexpr
paste
paste0
substr
str_split

basic functions
nchar():number of characters
tolower():convert to lower case
toupper():convert to upper case
casefold():case folding
chartr():character translation
abbreviate():abbreviation
substring():substrings of a character vector
substr():substrings of a character vec



print():generic printing.  argument quote=F
noquote():print with no quotes
cat():concatenation
format():special formats
toString():convert to string
sprintf():printing


pkg
stringr
nchar on factor fails. use str_length
str_trim

regex
Metacharacters
<!--
. the period or dot\\.
$the dollar sign\\$
*the asterisk or star\\*
+the plus sign\\+
?the question mark\\?
|the vertical bar or pipe symbol\\|
\the backslash\\\\
^the caret\\^
[the opening square bracket\\[
]the closing square bracket\\]
{the opening curly bracket\\{
}the closing curly bracket\\}
(the opening round bracket\\(
)the closing round bracket\\)
-->

encoding





R has five main types of objects to store data: vector, factor, matrix (and array), data.frame, and list.
character string

```{r}
clean_abb=function(string){
  string %>%
    gsub("\'s"," is", .) %>%
    gsub("\'m"," am", .) %>%
    gsub("\'ll"," will", .) %>%  
    gsub("isn\'t","is not", .) %>% 
    gsub("don\'t","do not", .) %>%
    gsub("aren\'t","are not", .) %>%
    gsub("ain\'t","are not", .) %>%
    gsub("didn\'t","did not", .) %>%
    gsub("shouldn\'t","should not", .) %>%
    gsub("wouldn\'t","would not", .) %>%
    gsub("couldn\'t","could not", .) %>>%
    trimws() %>>%
    return()
}
```

```{r, echo=F, eval=F}
    # gsub("’s"," is", .) %>%
    # gsub("’m"," am", .) %>%
    # gsub("’ll"," will", .) %>%  
    # gsub("isn’t","is not", .) %>% 
    # gsub("don’t","do not", .) %>%
    # gsub("aren’t","are not", .) %>%
    # gsub("ain’t","are not", .) %>%
    # gsub("didn’t","did not", .) %>%
    # gsub("shouldn’t","should not", .) %>%
    # gsub("wouldn’t","would not", .) %>%
    # gsub("couldn’t","could not", .) %>%
```

