---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cosmo
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pkg=c("tm")
sapply(pkg, require, character=T)
```


<h1>Text Mining</h1><ol type="I">

<h2><li>Handling and Processing Strings</li></h2><ol type="1">

<h3><li>Reading in Text Data</li></h3>
read text data in table format

read.table(): main function to read file in table format
read.csv(): reads csv files separated by a comma","
read.csv2(): reads csv files separated by a semicolon";"
read.delim(): reads files separated by tabs"\t"
read.delim2(): similar to read.delim()
read.fwf(): read fixed width format files

stringAsFactors=F

Raw text data
readLines()


<h3><li>String Manipulation</li></h3>


grep
gsub
gregexpr
paste
paste0
substr
str_split

basic functions
nchar():number of characters
tolower():convert to lower case
toupper():convert to upper case
casefold():case folding
chartr():character translation
abbreviate():abbreviation
substring():substrings of a character vector
substr():substrings of a character vec



print():generic printing.  argument quote=F
noquote():print with no quotes
cat():concatenation
format():special formats
toString():convert to string
sprintf():printing


pkg
stringr
nchar on factor fails. use str_length
str_trim

regex
Metacharacters
<!--
. the period or dot\\.
$the dollar sign\\$
*the asterisk or star\\*
+the plus sign\\+
?the question mark\\?
|the vertical bar or pipe symbol\\|
\the backslash\\\\
^the caret\\^
[the opening square bracket\\[
]the closing square bracket\\]
{the opening curly bracket\\{
}the closing curly bracket\\}
(the opening round bracket\\(
)the closing round bracket\\)
-->

encoding





R has five main types of objects to store data: vector, factor, matrix (and array), data.frame, and list.
character string

```{r}
clean_abb=function(string){
  string %>%
    gsub("aren\'t", "are not", .) %>%
    gsub("can\'t", "cannot", .) %>%
    gsub("couldn\'t", "could not", .) %>%
    gsub("didn\'t", "did not", .) %>%
    gsub("doesn\'t", "does not", .) %>%
    gsub("don\'t", "do not", .) %>%
    gsub("hadn\'t", "had not", .) %>%
    gsub("hasn\'t", "has not", .) %>%
    gsub("haven\'t", "have not", .) %>%
    gsub("he'd", "he would", .) %>% #"he had"
    gsub("he'll", "he will", .) %>% #, "he shall"
    gsub("he's", "he is", .) %>% #"he has", 
    gsub("i'd", "i would", .) %>% #"I had", 
    gsub("i'll", "i will", .) %>% #"I shall", 
    gsub("i'm", "i am", .) %>%
    gsub("i've", "i have", .) %>%
    gsub("isn\'t", "is not", .) %>%
    gsub("it's", "it is", .) %>% #"it has", 
    gsub("let's", "let us", .) %>%
    gsub("mustn\'t", "must not", .) %>%
    gsub("shan\'t", "shall not", .) %>%
    gsub("she'd", "she would", .) %>% #"she had", 
    gsub("she'll", "she will", .) %>% #"she shall", 
    gsub("she's", "she has", .) %>% #"she is", 
    gsub("shouldn\'t", "should not", .) %>%
    gsub("that's", "that is", .) %>% #"that has", 
    gsub("there's", "there is", .) %>% #"there has", 
    gsub("they'd", "they would", .) %>% #"they had", 
    gsub("they'll", "they will", .) %>% #"they shall", 
    gsub("they're", "they are", .) %>%
    gsub("they've", "they have", .) %>%
    gsub("we'd", "we would", .) %>% #"we had", 
    gsub("we're", "we are", .) %>%
    gsub("we've", "we have", .) %>%
    gsub("weren\'t", "were not", .) %>%
    gsub("what'll", "what will", .) %>% #"what shall", 
    gsub("what're", "what are", .) %>%
    gsub("what's", "what is", .) %>% #"what has", 
    gsub("what've", "what have", .) %>%
    gsub("where's", "where is", .) %>% #"where has", 
    gsub("who'd", "who would", .) %>% #"who had", 
    gsub("who'll", "who will", .) %>% #"who shall", 
    gsub("who're", "who are", .) %>%
    gsub("who's", "who is", .) %>% #"who has", 
    gsub("who've", "who have", .) %>%
    gsub("won\'t", "will not", .) %>%
    gsub("wouldn\'t", "would not", .) %>%
    gsub("you'd", "you would", .) %>% #"you had", 
    gsub("you'll", "you will", .) %>% #"you shall", 
    gsub("you're", "you are", .) %>%
    gsub("you've", "you have", .) %>%
    gsub("arent", "are not", .) %>%
    gsub(" cant ", " cannot ", .) %>%
    gsub("^cant ", "cannot ", .) %>%
    gsub(" cant$", " cannot", .) %>%
    gsub("couldnt", "could not", .) %>%
    gsub("didnt", "did not", .) %>%
    gsub("doesnt", "does not", .) %>%
    gsub(" dont ", " do not ", .) %>%
    gsub("^dont ", "do not ", .) %>%
    gsub(" dont$", " do not", .) %>%
    gsub("hadnt", "had not", .) %>%
    gsub("hasnt", "has not", .) %>%
    gsub("havent", "have not", .) %>%
    gsub(" isnt ", " is not ", .) %>%
    gsub("^isnt ", "is not ", .) %>%
    gsub(" isnt$", " is not", .) %>%
    gsub("mustnt", "must not", .) %>%
    gsub("shouldnt", "should not", .) %>%
    gsub("werent", "were not", .) %>%
    gsub(" wont ", " will not ", .) %>%
    gsub("^wont ", "will not ", .) %>%
    gsub(" wont$", " will not", .) %>>%
    trimws() %>>%
    return()
}
```

```{r, echo=F, eval=F}
clean_abb=function(string){
  string %>%
    gsub("\'s"," is", .) %>%
    gsub("\'m"," am", .) %>%
    gsub("\'ll"," will", .) %>%  
    gsub("isn\'t","is not", .) %>% 
    gsub("don\'t","do not", .) %>%
    gsub("aren\'t","are not", .) %>%
    gsub("ain\'t","are not", .) %>%
    gsub("didn\'t","did not", .) %>%
    gsub("shouldn\'t","should not", .) %>%
    gsub("wouldn\'t","would not", .) %>%
    gsub("couldn\'t","could not", .) %>>%
    trimws() %>>%
    return()
}
    # gsub("’s"," is", .) %>%
    # gsub("’m"," am", .) %>%
    # gsub("’ll"," will", .) %>%  
    # gsub("isn’t","is not", .) %>% 
    # gsub("don’t","do not", .) %>%
    # gsub("aren’t","are not", .) %>%
    # gsub("ain’t","are not", .) %>%
    # gsub("didn’t","did not", .) %>%
    # gsub("shouldn’t","should not", .) %>%
    # gsub("wouldn’t","would not", .) %>%
    # gsub("couldn’t","could not", .) %>%
```

